### 2020-03-04 doc/icfp20/intro.tex
final tweaks & swap figures
some more tweaks

To describe rules of basic harmonic structure,
\citet{magalhaes-harmtrace} and their successors use dependent types,
for example to index chords by major or minor mode.  However Haskell
currently has limited support for dependent types, and requires many
extentions and tricks such as the use of singleton
types~\citep{eisenberg-singleton}.

@@

>>>>

To describe rules of basic harmonic structure,
\citet{magalhaes-harmtrace} and their successors use dependent types,
for example to index chords by major or minor mode.  However Haskell
currently has limited support for dependent types, and requires many
extensions and tricks such as the use of singleton
types~\citep{eisenberg-singleton}.

@@

Our implementation is available as the anonymized supplement.

### 2020-03-04 doc/icfp20/music.tex
some more tweaks

\newcommand{\Interval}{
  \begin{figure}
  \includegraphics[width=12cm]{fig/interval.png} \\
  \begin{flushleft}
    \begin{footnotesize}
      \hspace{1.45cm} \texttt{per1 \hspace{0.5mm} min2  \hspace{2.5mm}
        maj2 \hspace{1.2mm} min3 \hspace{0.5mm} maj3 \ per4
        \hspace{1mm}aug4
        \hspace{0.5mm}  per5\hspace{1.2mm}  min6\hspace{1.6mm} maj6
        \hspace{1.6mm}min7\hspace{1.2mm} maj7\hspace{1.2mm} per8} \\
      consonant? \hspace{1.5mm} yes \hspace{4.2mm} no \hspace{6.5mm}  no
      \hspace{4.7mm} yes \hspace{3.8mm}  yes \hspace{3.7mm} no \hspace{3.5mm}
      no \hspace{4.3mm} yes \hspace{3.8mm} yes \hspace{3.2mm} yes
      \hspace{3.7mm} no \hspace{4mm} no \hspace{3.8mm} yes
    \end{footnotesize}
  \end{flushleft}
  \caption{13 Kinds of Intervals}
  \Description{13 Kinds of Intervals}
  \label{fig:interval}
 \end{figure}
}

@@

The most basic concept in melody is \emph{pitches}, which tell us
how high or low a tone is.
We represent pitches as natural numbers, but throughout the paper,
we use a more readable notation \texttt{name octave}, where
\texttt{name} ranges over \texttt{c}, \texttt{d}, \texttt{e}, etc.,
and \texttt{octave} denotes which octave the pitch belongs to.
For instance, the middle C is represented as \texttt{c 5}.

@@

For rhythm, the fundamental concept is \emph{duration}, an
unspecified unit of time during which a sound or silence lasts.
Examples of duration include whole, half, and quarter;
we define them simply as natural number constants.

>>>>

\newcommand{\Interval}{
  \begin{figure}
  \includegraphics[width=12cm]{fig/interval.png} \\
  \begin{flushleft}
    \begin{footnotesize}
      \hspace{1.45cm} \texttt{per1 \hspace{0.5mm} min2  \hspace{2.5mm}
        maj2 \hspace{1.2mm} min3 \hspace{0.5mm} maj3 \ per4
        \hspace{1mm}aug4
        \hspace{0.5mm}  per5\hspace{1.2mm}  min6\hspace{1.6mm} maj6
        \hspace{1.6mm}min7\hspace{1.2mm} maj7\hspace{1.2mm} per8} \\
      consonant? \hspace{1.5mm} yes \hspace{4.2mm} no \hspace{6.5mm}  no
      \hspace{4.7mm} yes \hspace{3.8mm}  yes \hspace{3.7mm} no \hspace{3.5mm}
      no \hspace{4.3mm} yes \hspace{3.8mm} yes \hspace{3.2mm} yes
      \hspace{3.7mm} no \hspace{4mm} no \hspace{3.8mm} yes
    \end{footnotesize}
  \end{flushleft}
  \caption{Intervals Within  an Octave}
  \Description{Intervals Within an Octave}
  \label{fig:interval}
 \end{figure}
}

@@

One of the most basic concepts in music is \emph{pitches}, which tell us
how high or low a tone is.
We represent pitches as natural numbers, but throughout the paper,
we use a more readable notation \texttt{name octave}, where
\texttt{name} ranges over \texttt{c}, \texttt{d}, \texttt{e}, etc.,
and \texttt{octave} denotes which octave the pitch belongs to.
For instance, the middle C is represented as \texttt{c 5}.

@@

\emph{Duration} is a fundamental concept for rhythm, denoting an
unspecified unit of time during which a sound or silence lasts.
Examples of duration include whole, half, and quarter;
we define them simply as natural number constants.
